Using CopyKAT to identify tumor cells in Ewing sarcoma samples

### 2024-06-14 analyses/cell-type-ewings/template_notebooks/03-copykat.Rmd
add mean cnv detection to copykat output

readr::write_tsv(celltype_df, copykat_results_file)
```

>>>>

all_info_df <- cnv_df |> 
  dplyr::select(barcodes,
                mean_cnv_detection) |> 
  dplyr::group_by(barcodes) |>
  dplyr::mutate(mean_cnv_detection = mean(mean_cnv_detection)) |> 
  dplyr::distinct() |> 
  dplyr::left_join(celltype_df)

readr::write_tsv(all_info_df, copykat_results_file)
```
